\appendix

\chapter{Installation Guidelines}

Using a UNIX terminal, navigate to the source code folder on the CD:

\texttt{cd code}

If no CD is available, the project can be cloned from the public Github repository (\texttt{git} required):

\texttt{git clone https://github.com/JonnyBurger/ddos-bachelor-thesis \&\& cd code}

If the  \texttt{node} command is not installed, install it from \url{https://nodejs.org}. The project has been tested with version 8.1.1 of node.js (\texttt{node -v} to see the version).

As the last step, the dependencies need to be installed:

\texttt{npm install}

The successful installation can be verified using:

\texttt{node index}

The above command also gives a help message to which commands can be used.

The test suite can be run using the following command:

\texttt{npm test}

\chapter{Open Source statement}

The source code of this project is open source and available under \url{https://github.com/JonnyBurger/ddos-bachelor-thesis}.

All code is licensed under the MIT license, whose full text can be found under \url{https://github.com/JonnyBurger/ddos-bachelor-thesis/blob/master/code/LICENSE}.

\chapter{Contents of the CD}


\textbf{Abstract.txt}: Abstract in English in plain text.

\textbf{Bachelorarbeit.pdf}: This thesis in PDF format.

\textbf{code/}: The source code of the project.

\textbf{Raw data.xlsx}: Excel spreadsheet containing all the raw data and calculations needed to create the figures.

\textbf{Related Work/}: A collection of related work papers.

\textbf{tex/}: The source code for this document.


\textbf{Zusfsg.txt}: Abstract in German in plain text.
