\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{Ethereum} Ethereum: Blockchain App Platform. \url{https://ethereum.org/}

\bibitem{DDoSRise} Author: Steve Mansfield-Devine. The Growth and Evolution of DDoS. Network
Security 10 (2015), pp. 13-20.

\bibitem{DDoSOverview} Authors: O. Osanaiye, K. Raymond Choo, M. Dlodlo. Distributed denial of service (DDoS) resilience in cloud: Review and conceptual cloud DDoS mitigation framework. 2016 \url{http://www.sciencedirect.com/science/article/pii/S1084804516000023}

\bibitem{DefCOM} Authors: G. Oikonomou, J. Mirkovic, P. Reiher, M. Robinson. A Framework for A Collaborative DDoS Defense. 2006. \url{https://www.acsac.org/2006/papers/123.pdf}

\bibitem{IETFDraft}Authors: K. Nishizuka, L. Xia, J. Xia, D. Zhang, L. Fang, C. Gray, R. Compton. Inter-organization cooperative DDoS protection mechanism \url{https://tools.ietf.org/html/draft-nishizuka-dots-inter-domain-mechanism-02}, Dezember 27, 2016

\bibitem{OriginalPaper} Authors: B. Rodriguez, T. Bocek, A. Lareida, D. Hausheer, S. Rafati, B. Stiller. A Blockchain-based Architecture for Collaborative DDoS Mitigation with Smart Contracts and SDN, 2017

\bibitem{IPv4Exhaustion} RIPE Network Coordination Centre: IPv4 Exhaustion. 2015 \url{https://www.ripe.net/publications/ipv6-info-centre/about-ipv6/ipv4-exhaustion}

\bibitem{EIP74} Author: Alex Beregszaszi. Ethereum Improvement Proposal 74: Support RSA signature verification. \url{https://github.com/ethereum/EIPs/issues/74}

\bibitem{BaselineRequirements} Baseline Requirements Certificate Policy for the Issuance and Management of Publicly-Trusted Certificates \url{https://cabforum.org/wp-content/uploads/CA-Browser-Forum-BR-1.4.5.pdf}

\bibitem{GlobalSign} GlobalSign: Securing a Public IP Address - SSL Certificates
\url{https://support.globalsign.com/customer/portal/articles/1216536-securing-a-public-ip-address---ssl-certificates}

\bibitem{Solc} The Solidity Contract-Oriented Programming Language
\url{https://github.com/ethereum/solidity}


\bibitem{Truffle} Truffle Framework \url{http://truffleframework.com/}

\bibitem{Solium} Solium Framework \url{https://github.com/duaraghav8/Solium}

\bibitem{ThinkingAboutSmartContractSecurity} Autor: V. Buterin, \url{https://blog.ethereum.org/2016/06/19/thinking-smart-contract-security}, 19. Juni 2016.


\bibitem{EIP150} Author: Vitalik Buterin. Ethereum Improvement Proposal 150: Long-term gas cost changes for IO-heavy operations to mitigate transaction spam attacks. \url{https://github.com/ethereum/EIPs/issues/150}


\bibitem{DefaultGoEthereumConfiguration} go-ethereum Github Repository. File \texttt{eth/config.go}. \url{https://github.com/ethereum/go-ethereum/blob/fff16169c64a83d57d2eed35b6a2e33248c7d5eb/eth/config.go\#L45}

\bibitem{ETHGasStationAnnouncement} Author: @ethgasstation. The Safe Low Gas Price \url{https://medium.com/@ethgasstation/the-safe-low-gas-price-fb44fdc85b91}



\end{thebibliography}

