\section{Cost estimation for DDoS mitigation}

The price that to pay for contracts varies as the contracts are developed and the gas and ether prices change, but it is possible to estimate the magnitude.

For a contract that stores IP addresses directly, the gas estimate was $ Deploy\ cost = 700113\ gas$ . The cost of adding 1 IP in a transaction is 104046 gas. When adding 2 IP addresses in the same transaction, 1 transaction gas cost of 21000 is saved among other minor savings.  The maximum is 46 IP addresses, after that the block gas limit is reached (which, theoretically, users of the network can increase) and another transaction has to be done. In our case, the cost is $ Add \ IP\ Cost = 66322 $ per IP and $ Transaction\ cost = 22660 $ per transaction. The price to store $ x $ IP addresses is in Equation \ref{eq:PriceToStoreXIPAddressed}.

\begin{equation}
c = Deploy\ cost + (x \cdot Add\ IP\ Cost) + \lceil\frac{x}{2}\rceil \cdot Transaction\ cost)
\label{eq:PriceToStoreXIPAddressed}
\end{equation}

In a expensive case where the Ether price is expensive $ ETH = \$100 $ and the user wants fast transactions $ \alpha = \alpha_{fast} $, it costs \$3.82 to do one transaction with 20 IP addresses ($ C \approx 1364194 $).

In a cheap case where Ether is reasonably cheap $ ETH = \$50 $ and most nodes have started accepting cheaper transactions $ a = a_{cheap} $, the transaction costs \$0.13.

So far users of the Ethereum network have not reacted to the higher Ether price by lowering gas costs. With activist sites like ethgasstation.info spreading awareness, it is realistic that users over time react and adjust the gas price according to the Ether price. If ether is higher, the gas price should be lower.

Using $ \alpha = 0.16 $ as the gas price (the value that etherchain.org deems as the equilibrium as of writing) and an Ether price of $ ETH = \$90 $ (the price at the same time), the result is a transaction cost of \$1.96.

For a contract that stores a pointer to a web resource containing IP addresses, there is a flat cost whenever the list is updated. The $Deploy\ cost$ still applies. The transaction cost for adding a URL with 64 characters was $ Transaction\ cost = 121466 $ in our test. This gives Equation \ref{eq:PointerCost}.

\begin{equation}
    C = Deploy\ cost + \#\ of\ transactions \cdot Transaction\ cost
    \label{eq:PointerCost}
\end{equation}
